Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_ssec_ontology.tex
half way to be done...
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@875 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsection{Simplified Model/Ontology (Knud)}
\label{ssec:ontology}
The model used to define the web service wrappers within this application has been influenced by WSDL, the main web service definition language, and some semantic-enriched approaches such as WSMO and OWL-S. There is no need to reinvent the wheel,

A WSDL operation is mapped to an action. Its inputs and outputs are called pre-postconditions (a WSMO concept).

This section could talk about a the part of the ontology describing the back-end services, how we remove the unnecessary information from WSDL and similar (not need anymore because the code has been generated), however we reuse some of the concepts from these technologies to define them (preconditions, postconditions, actions, and so on) allowing discovery and composition.

%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=8.31cm]{uddi.png}
%	\caption{UDDI overview}
%	\label{fig:uddi}
%\end{figure}

>>>>

\subsection{Conceptual Model}
\label{ssec:ontology}
The conceptual model used to define the web service wrappers within this application has been influenced by WSDL, the main web service definition language, and some semantic-enriched approaches such as WSMO and OWL-S. It belongs to a more complex conceptual model for FAST, which can be grouped into three levels: the gadget and screenflow level at the top, the level of individual screens in the middle, and the level of web services at the bottom. In a few words, a screenflow is a runnable set of screens, and a screen is a executable set of building blocks with a specific purpose. This section only describes in detail the former level, defining the different components a screen comprises. These three different kinds of screen components are form, operator and resource, and share the same structure. Any screen component has a set of actions, which need a set of preconditions (inputs) to be fulfilled in order to execute the action (operation in WSDL), and provides a set of postcondition (ouputs). These pre- and post-conditions are defined as individual RDF triples. This means that conditions, which are sets of facts, can be modelled as graph patterns using SPARQL notation \cite{sparql2008spec}, where a statement like ``there exists a sioc:User'' will be transformed into a simple pattern like ``a variable ?user is of type sioc:User''.
